---
title: "Part_3_Webapp"
author: "Marilena Melas"
date: "October 10, 2017"
output: html_document
runtime: shiny
---
title	author	date	output	runtime
Bash
Marilena Melas
10/10/2017
html_document
shiny
This is the third R Markdown for the midterm assignment. In this example, you will create a Shiny App using diamonds that you will initate by diamonds<-diamonds. It is worth 32 points if completed in full. The violin plot should let one choose their X-axis, Y-axis, Color-axis, Colorscale.

Create this Violin Plot Designer

http://www.sthda.com/english/wiki/ggplot2-violin-plot-quick-start-guide-r-software-and-data-visualization

Snapshot of your final version

This is just an image - don't let that confuse you.

image: That was just an image. If you are confused then just click on this link that comes next.

Example Fully Working Version

What you will create - an example if you click me

Please revise to diamonds

I have provided a script that gets you started and insures you don't get hung up on some details while still understanding concepts. Please note that you need to use aes_string as I've done to convert the retuned variable to a string.

For the color schemes, the more the better - but you could choose different at http://ggplot2.tidyverse.org/reference/scale_brewer.html

The script below needs a lot of editing to get it to diamonds. If you think it looks like a pain to edit, the first version of this exam I didn't include it. Also, the coloring doesn't work - but all you have to do is go to one line on this page and just add it (6 points off if its published without the color working)

```{r}
library(shiny)
library(ggplot2)
library(RColorBrewer)
diamonds<-diamonds
summary(diamonds)
iris<-iris
summary(iris)
```

```{r}
ui <- fluidPage(
  fluidRow(
    column(2,
      radioButtons("colorscale", "colorscale:",
               c("BrBG" = "BrBG",
                 "Dark2" = "Dark2",
                 "BuGn" = "BuGn")),        
         radioButtons("xaxis", "X-axis:",
               c("color" = "color",
                 "clarity" = "clarity",
                 "cut" = "cut")),
                 
            radioButtons("yaxis", "Y-axis:",
               c("price" = "price",
                 "depth" = "depth",
                 "table" = "table")),
                      
         radioButtons("color", "Color-axis:",
                 c("color" = "color",
                   "clarity" = "clarity",
                   "cut"="cut",
                   "price" = "price",
                   "depth" = "depth",
                   "table" = "table"))
    ),
    column(10,
      plotOutput("distPlot")
    )
  )
)
# Define server logic required to draw a histogram

server <- function(input, output) {
  output$distPlot <- renderPlot({
      diamonds    <- diamonds
      xaxis <- input$xaxis
      yaxis <- input$yaxis
      zaxis <- input$color
      cbrewer <- input$colorscale
      palette <- brewer.pal(8, cbrewer)
      ggplot(diamonds, aes_string(x = xaxis, y = yaxis)) + geom_violin(aes_string(fill = zaxis)) + scale_fill_manual(values = palette)
   })
}
# Run the application 

```{r}
shinyApp(ui = ui, server = server)
cat("
<style>
h1 {
    background-color: #990000;
    color:#FFF;
    text-align:center;
}
h2 {
   background-color:#f3d6d6;
   text-align:center;
   color:#333
}
h3 {
   margin-left:-5px;
   color:#333
}

</style>
")
```


© 2017 GitHub, Inc.
Terms
Privacy
Security
Status
Help
Contact GitHub
API
Training
Shop
Blog
About